%-------------------------
% Resume in Latex
% Author : Jorge Saravia
% Based off of: https://github.com/jakegut/resume
% License : MIT
% Edit : Alejandro Mosquera
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Alejandro Cardona Mosquera} \\ \vspace{8pt}
    \href{tel:+573188112557}{\underline{\faicon{phone} \small +(57) 318-8112557}} $|$ 
    \href{mailto:alejo13580@gmail.com}{\underline{\faicon{envelope} alejo13580@gmail.com}} $|$ 
    \href{https://linkedin.com/in/alejandro-c-mosquera/}{\underline{ \faicon{linkedin} linkedin.com/in/alejandro-c-mosquera/}}
\end{center}
\begin{center}
  %\href{https://github.com/AxzelBC}{\underline{ \faicon{github} github.com/AxzelBC}} $ (current job)|$
  \href{https://github.com/AxzelBC}{\underline{\faicon{github} github.com/AxzelBC}} $(personal)$
  
\end{center}


%-----------Introduction-----------
\section{Introduction}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hello, Hello!}{}
      {}{}
      {Technology professional with extensive experience in server administration, software development, process automation, and DevOps operations. Skilled in implementing complex technological solutions, ranging from academic platform management to enterprise application development and managing continuous deployments in local and international environments.}
      {}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidad del Valle (UNIVALLE)}{Cali, Colombia}
      {Information Systems Technology}{Feb. 2020 -- Oct. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Junior DevOps}{Feb. 2024 -- Present}
  {VELAIO SAS}{Cali, Colombia}
  \resumeItemListStart
    \resumeItem{Automated website deployments in diverse technologies (Drupal, Wordpress, VueJS, Laravel, .NET, Angular) using Azure DevOps.}
    \resumeItem{Managed Linux and Windows servers for local and international clients, such as CVC and Sodexo (Pluxee Group), ensuring application availability and security.}
    \resumeItem{Implemented pipelines for continuous integration and deployment in .NET Framework, Angular, and Kotlin projects, as well as application containerization and static code testing with SonarQube.}
  \resumeItemListEnd

  \resumeSubheading
    {.NET Developer}{Nov. 2023 -- Feb. 2024}
    {LD ASESORES}{Cali, Colombia}
    \resumeItemListStart
      \resumeItem{Designed and developed automation tools for accounting systems like Contapyme and Orion, using .NET Framework and ASP.NET Core with a TDD approach in MVC architectures.}
      \resumeItem{Managed a Windows server with IIS, ensuring the stability and performance of critical applications. Also implemented batch scripts for task automation.}
      \resumeItem{Created GitLab pipelines for CI/CD process automation, optimizing the software development lifecycle.}
    \resumeItemListEnd

    \resumeSubheading
    {Web Development Intern}{Mar. 2023 -- Sept. 2023}
    {VELAIO SAS}{Cali, Colombia}
    \resumeItemListStart
      \resumeItem{Implemented SCRUM methodology for the analysis and design of information systems, facilitating agile and efficient project development.}
      \resumeItem{Developed automation functions and application integrations using Deluge Script and workflows in Zoho Flow, improving operational efficiency.}
      \resumeItem{Created reports and dashboards in Zoho Analytics using SQL and developed web APIs with ASP.NET, applying CQRS architectures and TDD development approaches.}
    \resumeItemListEnd

    \resumeSubheading
    {Support Monitor}{Jan. 2022 -- Feb. 2023}
    {Universidad del Valle}{Cali, Colombia}
    \resumeItemListStart
      \resumeItem{Managed an Apache server with MySQL database using the XAMPP technology stack, ensuring the optimal operation of the Moodle LMS for graduate admission exams.}
      \resumeItem{Managed a Joomla-based website, divided into multiple sections for 7 graduate programs and 2 undergraduate programs, ensuring its continuous operation and site configuration.}
      \resumeItem{Configured connection points for routers, optimizing institutional network connectivity and security.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------Certifications-----------
\section{Certifications}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Microsoft Certified: Azure Fundamentals}{Microsoft}
      {https://learn.microsoft.com/en-us/users/alejandromosquera-5122/credentials/4c357d3e2698f58a}{September 2024}
  \resumeSubHeadingListEnd
  
  \resumeSubHeadingListStart
    \resumeSubheading
      {UBUNTU Linux Server}{Udemy}
      {ude.my/UC-4cc0912f-5657-42f3-b130-88ed638c3ae2}{July 2024}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {Docker Course For Beginners}{Udemy}
      {ude.my/UC-e7c35d6a-71fb-4d66-9658-cf865cd40b1c}{May 2023}
  \resumeSubHeadingListEnd



%

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C\#, Python, Golang, JavaScript, SQL, Bash, PowerShell, Bicep (IaC)} \\
     \textbf{Frameworks}{: .Net Framework, ASP.NET Core, Django (DRF), Gin} \\
     \textbf{Tools}{: Git, Docker, AWS, Azure, Azure DevOps, GitLab, Github, SonarQube} \\
     \textbf{Other Skills}{: Jira, Scrum, Linux, Windows Server (IIS), Firebase, DevOps, Scripting}
    }}
 \end{itemize}

%-----------Languages-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: B2} \\
     \textbf{Spanish}{: C2 (Native)} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
